---
title: "Assignment 7 - Read large fixed file formats"
author: "Joakim Sjøhaug"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("./assignment-7.R")
library(rvest)
library(tidyverse)
library(lubridate)
```


## Large fixed file formats

In this assignment we will work with large fixed file formats from <i>Centers of Disease Control and Prevention (CDC)</i>.
Since the files are so huge we used a fixed file format read to extract only the columns we needed. The data was persisted
to a file named <i>extracted-<filename-cdc></i> with only the data we needed. This reduced the file size drastically.

## Proportion of boys to girls yearly

```{r plot, message=FALSE}
bg_pp
```
<p>The proportion of boys to girls births each year seems to be equal, with the amount of male births each
year to be around 52% and girl births 48%.<p>

## Average weight at birth by gender
```{r plot1, message=FALSE}
avg_w_g
```
<p>The plot shows that males tend to have a higher weight at birth than girls. </p>

## Proportion of boys to grils week day
```{r plot2, message=FALSE}
b_g_pp
```

<p>From the plot, we can see that almost the same amount of boys and girls are birth each day of the week. </p>